A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-08 body/abstract.tex
Add my comments to abstract

We address the issue of automatically planning discrete sequences of contacts
that characterize a multiped motion in an arbitrary cluttered environment.
To overcome the inherent combinatorial difficulty of this problem, we separate it
in two sub-problems: first, planning a guide path for the root of the robot and
then, generating relevant contacts along this path.
We propose theoritical contributions for each sub-problem, and implement them
as a complete contact planner. 
First, we propose a geometrical characterization of a guide trajectory, the "reachability condition", that guarantees that a
guide can be mapped into the contact manifold of the robot. With this condition, asserting the "true feasibility" 
of a guide path boils down to performing collision tests, thus avoiding the costful of explicit computation of balanced contact configurations, as opposed to previous approaches.
Then, we propose a sequential algorithm to extend a truly feasible path into a sequence of contacts. For each limb, an offline sampling approach,
independent from the environment, is run once and for all, and used at run time to provide efficiently candidate configurations for contact.
The best candidate is chosen according to user created heuristics. We propose two such heuristics, used in all our experiments, and 
designed for generic robotic applications: a manipulatibily based heuristic, EFORT, and a robustness criterion regarding the balance of the robot.
These contributions are implemented within the open source software Hpp. Our framework allows us to generate complex multi contact sequences for a large
variety of robots, including a HRP-2, Hyq, and a dextrous hand, with interactive performances.

>>>>

We address the issue of automatically planning discrete sequences of contacts
that characterize a multiped motion in an arbitrary cluttered environment.
To overcome the inherent combinatorial difficulty of this problem, we separate it
in two sub-problems: first, planning a guide path for the root of the robot and
then, generating relevant contacts along this path.
We propose theoretical contributions for each sub-problem, and implement them
as a complete contact planner. 
First, we propose a geometrical characterization of a guide trajectory, the ``reachability condition", which guarantees that a
guide can be mapped into the contact manifold of the robot. With this condition, asserting the``true feasibility" 
of a guide path boils down to performing collision tests, thus avoiding the expensive explicit computation of balanced contact configurations, as opposed to previous approaches.
Then, we propose a sequential algorithm to extend a truly feasible path into a sequence of contacts. For each limb, an offline sampling approach,
independent from the environment, is run once and for all, and used at run time to provide efficiently candidate configurations for contact.
The best candidate is chosen according to user-created \adnote{user-defined?} heuristics. We propose two such heuristics, used in all our experiments, and 
designed for generic robotic applications: a manipulatibily-based heuristic, EFORT, and a robustness criterion regarding the balance of the robot.
These contributions are implemented within the open-source software Hpp. Our framework allows us to generate complex multi-contact sequences for a large
variety of robots, including a HRP-2, Hyq, and a dextrous hand, with interactive performances.
